Paper_analyses

### 2021-08-02 Paper_Analyses_subj_obje_arousal.Rmd
back to it

# replace the values when neutral_pos and neutral_neg is FALSE respectivelly
# library(dplyr)
# check how many nas do we have before we start
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal))
 # FALSE   TRUE 
# 158193  13975 
tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
    mutate_at(vars(matches('^neutral_pos_.*$')), ~ 
                  replace(., neutral_pos == FALSE, NA))

@@

tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$)

>>>>

# replace the values when neutral_pos and neutral_neg is FALSE respectivelly
# library(dplyr)
# check how many nas do we have before we start
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal))
 # FALSE   TRUE 
# 158193  13975

# compute new varoables where arousal is scaled to negative (negative value - mean of negative and neutral) same to positive
tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
    mutate_at(vars(matches('^neutral_pos_.*$')), ~ 
                  replace(., neutral_pos == FALSE, NA))

@@

tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE, tmp.df4_full_stim_downs_jun2021_60bins)
